--
title: 'Quiz #4'
author: "Jessy Lin"
date: "2022-11-09"
output: html_document
---
1. open the mtcars dataset.
```{r}
data("mtcars")
```

2. Find the correlation between mpg and hp.
```{r}
cor(mtcars$mpg,mtcars$hp)
```

3. Create a scatterplot that matches your statistic in #2. 
```{r}
ggplot(mtcars, aes(mpg,hp)) +geom_point()
```
#need ggplot2 library
4. Find the correlation between am and mpg. Explain why you chose to use your specific function
```{r}
cor(mtcars$am,mtcars$mpg)
#I used this specific function because it tells you the strengthand direction of the relationship between am and mpg.
```

5. Run a regression to predict mpg from disp.
```{r}
lm(mpg~disp, mtcars)
```

6. Create a graph that displays your regression line. 
```{r}
ggplot(mtcars, aes(mpg,disp)) +geom_point() + geom_smooth(method = "lm")
```

7. Run a t test to compare the horse power of automatic and manual transmission cars. 
```{r}
t.test(mtcars$hp ~ mtcars$am)
```

8. Create a graph that accompanies your statistic in #6.
```{r}
q8<-lm(mpg~disp, mtcars)
plot(q8)
```

9. Run an ANOVA to predict disp from gear. 
```{r}
lm(disp~gear, mtcars)
q9<-lm(disp~gear, mtcars)
Anova(q9)
```

10. You have a multiple choice test that is 25 questions with 5 potential options. What type of test can you run to determine if your score of 16/25 differs from chance? 
```{r}
#The test that you can run is a binomial test because it determines if something happens more often than chance.
```

11. Run the test you described in #10
```{r}
binom.test(16,25, p=0.25)
```
#should be .2 
