
---
title: 'Quiz #5'
author: "Jessy Lin"
date: "2022-11-25"
output: html_document
---

For this assignment, you should fix the code below. Knit a copy and submit the knitted version via Canvas. 

## Problem 1
```{r}
ggplot(mtcars, aes(hp, disp))+ geom_point() +theme_classic()
```
#need ggplot2 library

## Problem 2
A student is trying to make a graph that shows a regression line for weight predicted by miles per gallon with this code: 

```{r}
ggplot(mtcars,aes(wt,mpg))+geom_point()+geom_smooth()+theme_classic()
```

## Problem 3

```{r}
library(tidyverse)
data("diamonds")
diamondsDE<-diamonds %>% filter(color== "D","E")

```
#need to use or statement

## Problem 4

```{r}
time<- sample(0:60, 5, replace=TRUE)
light1<- c(0,.25,.75,2.5,3.25,5.5,5.25,8,8.88,9,9.5,9.75,9.75)
light1<-sample(light1, 5, replace=TRUE)
light2<- c(0,0,0,0,0,0,0,0,.5,1.25,2,2.75,3.75,4.25)
light2<-sample(light2, 5, replace=TRUE)
scientistDat<- cbind.data.frame(time,light1,light2)
ggplot(scientistDat, aes(light2,time)) + geom_bar() + theme_bw()

```
#can't make a bar graph with two variables

## Problem 5
```{r}
lm1<- lm(light2~light1+time, scientistDat)
summary(lm1)
```

## Problem 6
```{r}
ggplot(mtcars, aes(hp, disp))+ geom_point()
```

## Problem 7 NOT DONE

```{r}
cwwide <- pivot_wider(ChickWeight, id_cols = c("chick", "diet"), names_from = "time", values_from = "weight")
```
#need to change capitalization 

## Problem 8

Compute the correlation between the transmission and mpg columns in the mtcars dataset.
```{r}
cor(mtcars$am, mtcars$mpg)
```

## Problem 9

Color the graph using disp as a third variable. 
```{r}
ggplot(mtcars, aes(hp, mpg, color=as.factor(disp))) + geom_point()
```

## Problem 10

```{r}
mtcars$vs2<- ifelse(mtcars$vs==0, "autonomic", "manual")
```

## Problem 11
```{r}
mlinearOne <- lm(mpg~disp+wt, mtcars)
summary(mlinearOne)
```

## Problem 12

You volunteer at an animal shelter and play with 10 tabby cats. The veterinarian tells you that a tabby cat has a 25% chance of being born with hazel eyes. If 5 of the tabby cats you saw had hazel eyes, did this differ from chance?
```{r}
binom.test(5, 10, p=.25)
```

## Problem 13

```{r}
data("USArrests")
summary(USArrests)

USArrests$HighorLow<-NA
for(i in 1:nrow(USArrests)){
  if(USArrests$Murder[i]>8){
    USArrests$HighorLow[i]<-"high"}
  else USArrests$HighorLow[i]<-"low"
}
```

## Problem 14

```{r}
summary(diamonds$cut)
recode_factor(diamonds$cut,"Fair"=1, "Good"=2, "Very Good"= 3)
```
#needs recode command 
## Problem 15

4. Open the starwars dataset. Run a summary function on those that are apart of the tatooine planet. Those from Tatooine, find how many characters have a birth year of exactly or over 50. Figure out how the fix the error(s): 
```{r}
data(starwars)
Tatooine <- subset(starwars, starwars$homeworld=="Tatooine")
summary(Tatooine)
TatOver50 <- Tatooine %>% select(birth_year<=50)
prow(TatOver50)
```
#what's p row? 
#filter would be a better choice 
## Problem 16

```{r}
cut_data<- cor(diamonds$cut, diamonds$price)
biserial.cor(cut_data$color, cut_data$price)

```
#can't use biserial here 

first, you must set your seed to the same one I do.

```{r}
set.seed()
```

#missing seed argument

Now that we have the same seed, we need the data to sample from

```{r}
person <- c("one","two","three","four","five","six","seven","eight","nine","ten")
favorite_number <- sample(1:1000000, 10, replace = TRUE)
animal <- c("cat","dog","axolotl")
persons_animal <- sample(animal, 10, replace = TRUE)
```

```{r}
theDataSet <- cbind.data.frame(person, favorite_number, persons_animal)
```

## Problem 18

```{r}
meanSdDev<- function(num1,num2){mean(num1)/sd(num2)}
```

## Problem 19
```{r}
Chickweight %>% select(chickweight,weight=50)

```
#need to capitalize chickweight dataset. need to use == not = 
## Problem 20 
```{r}
data("billboard")
billboardLong <- pivot_wider(billboard, cols = c(colnames(billboard[4:75])), names_to = "rankings", values_to = "weeks")
britney <- billboardLong %>% filter(artist == "Spears Britney") %>% na.omit(rankings)
nrow(britney$rankings)
```
#not fixed 
## Problem 21
Create a boxplot for price for the different carats
```{r}
ggplot(diamonds, aes(price, carat))+ geom_boxplot()
```
